---
title       : Gaussian comparison
subtitle    : Shiny example
author      : Data science specialization
job         : Coursera
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Motivation

The goal of this Shiny server is to illustrate a few possibilities:

1. Input parameters

2. Reactive functions

3. Plot output

--- .class #id 

## Chosen example

The application draws samples from 2 normal distributions, whose parameters are chosen by the user. It plots them for comparison.

### Inputs

The user chooses the parameters for the 2 normal disitributions and the number of points to draw.

### Outputs

The server outputs the histograms showing the overlap between the two distributions.

It also perfoms a 2 sample T-test and gives the 95% confidence interval for the difference between the means, and the p-value for a null difference.

--- .class #id 

## Results

It can be used to show that even with a lot of overlap, we can distinguish small differences if the number of points is large enough. E.g. $\mu_1 =0$ and $\mu_2=0.1$ for $\sigma=1$ and $n=1000$:

```{r, echo=FALSE, fig.height=2}
mu1 <- 0
sigma1 <- 1
n1 <- 1000

mu2 <- 0.1
sigma2 <- 1
n2 <- 1000

library(ggplot2)
draw1 <- data.frame( x = rnorm(n1,mean=mu1,sd=sigma1))
draw2 <- data.frame( x = rnorm(n2,mean=mu2,sd=sigma2))

p<- ggplot(data=draw1, aes(x=x))
p <- p + geom_histogram(binwidth=0.1, fill="red", alpha = 0.5)
p <- p + geom_histogram(data=draw2, aes(x=x), binwidth=0.1, fill="blue", alpha = 0.5)

print(p)
```

```{r}
result<-t.test(draw1$x, draw2$x)
result$conf.int[1:2]
result$p.value
```

